He-Man: A domain-specific language for lightweight concurrency

### 2012-03-06 paper/paper.tex
Excising some old text; added citation.

Our observation is that the event loop model, in programming languages parlance,
is essentially trampolining continuation-passing-style, which can be obtained by
mechanical translation from the straight-line threaded code. This suggests it is
possible to obtain the best of both worlds---a threaded programming model with
the performance of event loops.

@@

We will continue our work on He-Man, and hope to submit it to a programming
languages conference such as ICFP. Most importantly, we plan to rework our
front-end so as to reject badly-typed programs; currently, we do not ensure
that, e.g., we do not take the sum of two file handles.

@@

The backend can perform more aggressive optimization on the code blocks. In
particular, we currently do not allow any control flow except at tail position;
if both branches of an \t{if} are non-blocking, we should avoid translating it
into multiple blocks, requiring a yield to the main loop. It should also be
possible to gather interesting output from the backend, like a graphical
representation of the generated state machine, for documentation purposes.

>>>>

Our observation is that the event loop model is simply trampolining
continuation-passing-style, % TODO citation
which can be obtained by mechanical translation from the straight-line threaded
code. This suggests it is possible to obtain the best of both worlds---a
threaded programming model with the performance of event loops.

@@

@@
